---
title: "Visualisation of Drug Flows"
author: "Sefa Ozalp"
date: "2019-11-21"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This is a very brief document to visualise cocaine and heroine flows using a chord diagram using the data provided by my colleague, Luca Giommoni. I have attempted to keep this under an hour. 

```{r}
library(tidyverse)
library(circlize)
# devtools::install_github("mattflor/chorddiag")
```


# Heroin Data

```{r heroine, message=F, warning=F, fig.width=10, fig.height=10}
heroin_path <- here::here("data/heroin_circos.txt")
heroin_data <- read_tsv(heroin_path,col_names = T) 

hr_rownames <- heroin_data$ID

hr_data <- heroin_data %>% 
  mutate_all(~str_replace(., "-", "0")) %>% 
  select(-ID) %>% 
  data.matrix() 

rownames(hr_data) <- hr_rownames

hr_data %>% str()
chordDiagram(hr_data, transparency = 0.3)


```

# Cocaine Data
```{r cocaine, message=F, warning=F, fig.width=10, fig.height=10}


coke_path <- here::here("data/Cocaine.txt")
coke_data <- read_tsv(coke_path,col_names = T) 

ck_rownames <- coke_data$ID

ck_data <- coke_data %>% 
  mutate_all(~str_replace(., "-", "0")) %>% 
  select(-ID) %>% 
  data.matrix() 

rownames(ck_data) <- ck_rownames

ck_data %>% str()
chordDiagram(ck_data, transparency = 0.3)

```


Obviously the visalisations can be improved. Especially the margins and colours could use some editing. However, I've aimed to do keep this project under an hour, including the GitHub deployment so polishing will possible when I get back to this later. 

# Future Work: Improve Labels, chorddiag, and Sankey Diagram

